West Africa cuckoo stopover rainfall patterns

### 2018-07-13 stopover_rainfall_ndvi_detailcoords_vis.Rmd
Added code to graph TAMSAT rainfall

int_out<-read.csv('data/spring_rainfall_NDVI_GRIMMS_by_stopover_detailcoords_2018_dead.csv', h=T)

@@

temp=ggplot(data=t2,aes(x=variable, y=value))+
geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, ymax=500), fill='grey')+
    geom_line(data=t2, aes(x=variable, y=value2*500), colour='red')+
  geom_line(data=t2, aes(x=variable, y=aquaNDVI*500), colour='cyan')+
  geom_line(data=t2, aes(x=variable, y=terrNDVI*500), colour='orange')+
  geom_bar(stat='identity', colour='black')+
    geom_line(aes(y=cumrf), col='green', size=1)+
  facet_wrap(~country+SO_startDOY, scales='free_y')+theme_classic()+
  ylab('cumulative rainfall since 01 Jan (mm)')+ xlab('Day of year')+
          ggtitle(paste("Year:",i,"   PTT:", j, "   Arr date:", dtemp$arrive_breeding))+geom_label(data=lc1, aes(x=15, y=450, vjust=1,label=label), fill=NA)

>>>>

int_out<-read.csv('data/spring_rainfall_NDVI_GRIMMS_TAMSAT_by_stopover_detailcoords_2018_dead.csv', h=T)

@@

t2.tmcum<- t1.3 %>% group_by(ptt, year, SO_startDOY,country, key) %>% dplyr::summarise(tamRAIN=first(tamRAIN), variable=first(variable)) %>%
  dplyr::mutate(cumrfTAM=cumsum(tamRAIN))

temp=ggplot(data=t2,aes(x=variable, y=value))+
geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, ymax=500), fill='grey')+
    geom_line(data=t2, aes(x=variable, y=value2*500), colour='red')+
  geom_line(data=t2, aes(x=variable, y=aquaNDVI*500), colour='cyan')+
  geom_line(data=t2, aes(x=variable, y=terrNDVI*500), colour='orange')+
    geom_line(data=t2, aes(x=variable, y=aquaANOM*1000+200), colour='cyan', linetype=2)+
    geom_line(data=t2, aes(x=variable, y=terrANOM*1000+200), colour='orange', linetype=2)+
  geom_line(data=t2, aes(x=variable, y=tamRAINanom+200), colour='dark green', linetype=2)+
  geom_hline(yintercept=200)+
  geom_bar(stat='identity', colour='black')+
    geom_line(aes(y=cumrf), col='green', size=1)+
  geom_line(data=t2.tmcum, aes(x=variable, y=cumrfTAM), col='dark green', size=1)+
  facet_wrap(~country+SO_startDOY, scales='free_y')+theme_classic()+
  ylab('cumulative rainfall since 01 Jan (mm)')+ xlab('Day of year')+
          ggtitle(paste("Year:",i,"   PTT:", j, "   Arr date:", dtemp$arrive_breeding))+geom_label(data=lc1, aes(x=15, y=450, vjust=1,label=label), fill=NA)
